Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Corrected claim about multi-color MAPFM

	A related observation is that the algorithms introduced in this work in their current form do not rely on the property of agents and goals having one color (team). Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time. Future research could study the multi-color MAPFM generalization and the application of methods described in this work to that problem.

>>>>

	A related observation is that ICTS-m in its current form does not rely on the property of agents and goals having one color (team). It could easily be adapted to support one or more colors for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time. A multi-color generalization of exhaustive ICTS would require a different matching enumeration method. Future research could study the multi-color MAPFM generalization and the application of methods described in this work to that problem.
